Comparing tool variability and numerical variability in fMRI analyses

### 2021-11-11 paper/paper.tex
revises in method

\tristan{
Explain how the instrumentation was validated:
\begin{enumerate}
\item Verify that two consecutive IEEE executions are identical (no random effects)
\item Verify that all pipelines use libm
\item List all the dependencies of all the pipelines using ldd 
\item Verify that no math function is implemented in these dependencies
\item Verify that fuzzy libmat has an effect on the results
\end{enumerate}
}

@@

We measured between-tool (BT) variability by running the pipelines
described in~\cite{bowring2019exploring} with FSL version 5.0.10, AFNI
version 18.1.09, and SPM12 version r7771 executed with GNU/Octave version
5.2. All these software versions were identical to the study
in~\cite{bowring2019exploring} except for SPM for which we used Octave
instead of MATLAB to enable mathematical function instrumentation using
Fuzzy Libmath. Indeed, MATLAB uses its own built-in mathematical functions,
which prevents the use of Fuzzy Libmath. In AFNI, we set the number of
threads to 7 \discuss{to reproduce the results
in~\cite{bowring2019exploring} in a feasible execution time}. All the
analyses were conducted on the CentOS 7.3 operating system. The
computations were performed on \href{https://www.computecanada.ca}{Compute
Canada's} Béluga cluster nodes, each with 2$\times$ Intel Gold 6148 Skylake
@ 2.4 GHz (40 cores/node) CPU and 8~GB of RAM per core. We encapsulated the
above-mentioned software packages in Docker container images available at
\url{https://github.com/ali4006/fuzzy-neurotools/tree/main/dockerfile}
\tristan{Ali, could you put them in the paper repo unless there is a good
reason to keep them separate?}.

>>>>

To validate instrumentations, we verified that two consecutive IEEE executions are identical;
there are no randomness effects in all pipelines.
We also listed all the pipeline library dependencies using the ldd Linux utility.
We ensured that (1) all pipelines are dynamically linked to the libmath library
(2) there is no alternative implementation for the basic mathematical functions in these dependencies.
Finally, we verified that Fuzzy libmath affects computational results.

@@

We measured between-tool (BT) variability by running the pipelines
described in~\cite{bowring2019exploring} with FSL version 5.0.10, AFNI
version 18.1.09, and SPM12 version r7771 executed with GNU/Octave version
5.2. All these software versions were identical to the study
in~\cite{bowring2019exploring} except for SPM for which we used Octave
instead of MATLAB to enable mathematical function instrumentation using
Fuzzy Libmath. Indeed, MATLAB uses its own built-in mathematical functions,
which prevents the use of Fuzzy Libmath. In AFNI, we set the number of
threads to 7 \discuss{to reproduce the results
in~\cite{bowring2019exploring} in a feasible execution time}. All the
analyses were conducted on the CentOS 7.3 operating system. The
computations were performed on \href{https://www.computecanada.ca}{Compute
Canada's} Béluga cluster nodes, each with 2$\times$ Intel Gold 6148 Skylake
@ 2.4 GHz (40 cores/node) CPU and 8~GB of RAM per core. We encapsulated the
above-mentioned software packages in Docker container images available at
\url{https://github.com/big-data-lab-team/fuzzy-neurotools}.
